---
title: "R Notebook"
output: 
  md_document:
    variant: markdown_github
---

```{r}
options(warn = -1)
library(ISLR)
summary(Weekly)
```
```{r}
attach(Weekly)
set.seed(1)

```

Fit a logistic regression model that predicts `Direction` using `Lag1` and `Lag2`

```{r}
glm.fit = glm(Direction ~ Lag1 + Lag2, data = Weekly, family = binomial)
summary(glm.fit)
```

Fit a logistic regression model that predicts `Direction` using `Lag1` and `Lag2` using all but the first observation.

```{r}
glm.fit = glm(Direction ~ Lag1 + Lag2, data = Weekly[-1,], family = binomial)
summary(glm.fit)
```

Use the above model to predict the direction of the first observation.

```{r}
glm_probs = predict(glm.fit, Weekly[1,], type = "response")
ifelse(glm_probs > 0.5, "Up", "Down")
```

Prediction was UP, true Direction was DOWN.

`cv.glm()` function can be used to compute LOOCV error rate but here we're gonna use `glm()` and `predict.glm()`
functions to do the same thing.

```{r}

err_count = NULL
for(i in 1:dim(Weekly)[1]){
  glm.fit = glm(Direction ~ Lag1 + Lag2, data = Weekly[-i, ], family = binomial)
  is_up = predict.glm(glm.fit, Weekly[i, ], type = "response") > 0.5
  is_true_up = Weekly[i, ]$Direction == "Up"
  err_count[i] = ifelse(is_up != is_true_up, 1, 0)
}
sum(err_count)
```
```{r}
mean(err_count)
```

LOOCV estimates a test error rate of 45%.

```{r}
detach(Weekly)
```

