---
title: "R Notebook"
output: 
  md_document:
    variant: markdown_github
---

```{r}
library(MASS)
summary(Boston)
```

a. an estimate for the population mean of `medv`
```{r}
mu_hat = mean(Boston$medv)
mu_hat
```

b. estimate of the standard error of `mu_hat`
```{r}
mu_err = sd(Boston$medv)/ sqrt(length(Boston$medv))
mu_err
```

c. Now estimate the standard error of `mu_hat` using the bootstrap.
```{r}
library(boot)
boot.fn = function(data, index) {
  return(mean(data[index]))
}
btstrap = boot(Boston$medv, boot.fn, 1000)
btstrap
```

Similar to answer from (b) up to two significant digits. (0.4020 vs 0.4089)

95 % confidence interval for the mean of `medv`

`[ˆμ − 2SE(ˆμ), μˆ + 2SE(ˆμ)]`
```{r}
conf_int = c(mu_hat - 2*0.4020, mu_hat + 2*0.4020)
conf_int

```

Compare it to the results obtained using `t.test(Boston$medv)`
```{r}
t.test(Boston$medv)
```

Boostrap estimate equal to t-test upto two decimal places.

```{r}
medv.med = median(Boston$medv)
medv.med
```

We now would like to estimate the standard error of `ˆμmed`. Unfortunately, there is no simple formula for computing the standard error of the median. Instead, estimate the standard error of the median using the bootstrap.
```{r}
boot.fn = function(data, index) return(median(data[index]))
boot(Boston$medv, boot.fn, 1000)
```

Median of 21.2 with SE of 0.380. Small standard error relative to median value.

an estimate for the tenth percentile of `medv` in Boston suburbs
```{r}
medv_tenth = quantile(Boston$medv, c(0.1))
medv_tenth
```

Use the bootstrap to estimate the standard error for above.
```{r}
boot.fn = function(data, index) return(quantile(data[index], c(0.1)))
boot(Boston$medv, boot.fn, 1000)
```

Tenth-percentile of 12.75 with SE of 0.511. Small standard error relative to tenth-percentile value.
